The five axes of the Turtle: symmetry and asymmetry in NGC~6210

### 2020-12-03 ms.tex
More dealing with point 9
Write up the description of the worst-case scenario for the systematic
error in the knot proper motions.  Re-do Table 2 and the Figure of
velocity versus radius.

    NE Blue complex & 60 & \AxM{E}(iii) & -51 \pm 1 & 23 \pm 5 & 65 \pm 2 & -69 \pm 4 & 5 \pm 1 & 0.14 \pm 0.04 & 2.1 \pm 0.6\\

@@

    SW Red complex & 250 & \AxP{E}(iii) & +38 \pm 1 & 18 \pm 3 & 49 \pm 2 & 68 \pm 3 & 7 \pm 2 & 0.19 \pm 0.06 & 3.7 \pm 1.2\\
    NE Red complex & 30 & \AxP{E}(ii) & +25 \pm 2 & 5 \pm 4 & 30 \pm 2 & 81 \pm 7 & 4 \pm 1 & 0.26 \pm 0.21 & 8.0 \pm 6.7\\
    SW Faint Blue & 225 & \AxM{E}(ii) & -26 \pm 1 & 26 \pm 4 & 41 \pm 3 & -50 \pm 4 & 7 \pm 1 & 0.11 \pm 0.02 & 2.6 \pm 0.5\\

@@

    NW knot  & 310 & \AxP{E}(i) & +18 \pm 1 & 11 \pm 8 & 24 \pm 4 & 63 \pm 17 & 8 \pm 1 & 0.18 \pm 0.10 & 6.7 \pm 4.5\\
    NW Red complex & 300 & \AxP{E}(i) & +21 \pm 2 & 10 \pm 4 & 27 \pm 3 & 68 \pm 8 & 6 \pm 2 & 0.16 \pm 0.08 & 6.0 \pm 3.1\\

@@

    SE Blue complex & 135 &  \AxM{E}(i) & -31 \pm 3 & 39 \pm 10 & 54 \pm 8 & -44 \pm 8 & 5 \pm 1 & 0.07 \pm 0.02 & 1.1 \pm 0.4\\
    SE knot & 135 & \AxM{E}(i) & -35 \pm 3 & 39 \pm 10 & 57 \pm 7 & -47 \pm 8 & 6 \pm 1 & 0.09 \pm 0.02 & 1.5 \pm 0.4\\

@@

This dichotomy between the two arms of axis~E
is such a surprising result that it is important to establish how robust it is in the face of the uncertainties in our analysis.
The kinematic ages depend on the plane-of-sky positions and proper motions (columns 8 and 5 of Table~\ref{tab:3d}),
and the uncertainties in the proper motions are of two types: random and systematic.
The random uncertainties for individual features are quite large,
greater than 50\% for the \AxP{E} axis and \(\approx 30\%\) for the \AxM{E} axis,
but these can be reduced by aggregating multiple independent measurements.
For instance, by averaging all of the features
associated with each arm of the axis,
we find \(t_{\text{kin}}(\AxP{E}) = \SI{6.7 \pm 1.6}{kyr}\) 
versus \(t_{\text{kin}}(\AxM{E}) = \SI{1.6 \pm 0.2}{kyr}\),
which significantly differ by more than \(3\sigma\).
However, this does not account for the systematic uncertainty
in the image alignment between observational epochs,
which we estimate to be equivalent to
\SI{1.5}{arcsec.yr^{-1}} or \SI{\pm 14}{km.s^{-1}}
(see section~\ref{sec:proper-motions}).
We therefore consider a worst-case scenario in which a shift of this magnitude
is applied along \(\text{PA} = \ang{315}\),
which is the average projected axis of the knot outflow.
Repeating all the proper motion measurements for this then yields
\(t_{\text{kin}}(\AxP{E}) = \SI{3.7 \pm 0.5}{kyr}\) 
versus \(t_{\text{kin}}(\AxM{E}) = \SI{2.3 \pm 0.3}{kyr}\).
The difference between the timescales of the positive and negative axes is smaller in this scenario, \(\SI{1.4 \pm 0.6}{kyr}\),
but it is still significant at the \(2\sigma\) level.

>>>>

    NE Blue complex & 60 & \AxM{E}(iii) & -51 \pm 1 & 24 \pm 3 & 66 \pm 2 & -69 \pm 2 & 5 \pm 1 & 0.14 \pm 0.01 & 2.0 \pm 0.2\\

@@

    SW Red complex & 250 & \AxP{E}(iii) & +38 \pm 1 & 17 \pm 4 & 49 \pm 2 & 70 \pm 4 & 7 \pm 2 & 0.20 \pm 0.04 & 3.9 \pm 0.9\\
    NE Red complex & 30 & \AxP{E}(ii) & +25 \pm 2 & <8 & 31 \pm 1 & > 75 & 4 \pm 1 & > 0.15  & >5\\
    SW Faint Blue & 225 & \AxM{E}(ii) & -26 \pm 1 & 17 \pm 10 & 36 \pm 5 & -61 \pm 14 & 7 \pm 1 & 0.14 \pm 0.02 & 3.9 \pm 2.2\\

@@

    NW knot  & 310 & \AxP{E}(i) & +18 \pm 1 & < 14 & 23 \pm 2 & >57 & 8 \pm 1 & > 0.15  & > 5\\
    NW Red complex & 300 & \AxP{E}(i) & +21 \pm 2 & 7 \pm 4 & 26 \pm 3 & 74 \pm 9 & 6 \pm 2 & 0.22 \pm 0.12 & 8.6 \pm 4.9\\

@@

    SE Blue complex & 135 &  \AxM{E}(i) & -31 \pm 3 & 32 \pm 11 & 49 \pm 8 & -49 \pm 10 & 3 \pm 2 & 0.05 \pm 0.02 & 0.9 \pm 0.3\\
    SE knot & 135 & \AxM{E}(i) & -35 \pm 3 & 42 \pm 3 & 59 \pm 3 & -45 \pm 3 & 5 \pm 1 & 0.07 \pm 0.02 & 1.1 \pm 0.1\\

@@

This dichotomy between the two arms of axis~E
is such a surprising result that it is important to establish how robust it is in the face of the uncertainties in our analysis.
The kinematic ages depend on the plane-of-sky positions and proper motions (columns 8 and 5 of Table~\ref{tab:3d}),
and the uncertainties in the proper motions are of two types: random and systematic.
The random uncertainties for individual features are quite large,
greater than 50\% for the \AxP{E} axis and \(\approx 30\%\) for the \AxM{E} axis,
but these can be reduced by aggregating multiple independent measurements.
For instance, by averaging all of the features
associated with each arm of the axis,
we find \(t_{\text{kin}}(\AxP{E}) = \SI{6.7 \pm 1.6}{kyr}\) 
versus \(t_{\text{kin}}(\AxM{E}) = \SI{1.6 \pm 0.2}{kyr}\),
which differ by more than \(3\sigma\).
However, this does not account for the systematic uncertainty
in the image alignment between observational epochs,
which we estimate to be equivalent to
\SI{1.5}{arcsec.yr^{-1}} or \SI{\pm 14}{km.s^{-1}}
(see section~\ref{sec:proper-motions}).
We therefore consider a scenario in which a shift of this magnitude
is applied between the two epochs of \textit{HST} observations.
The shift is applied along \(\text{PA} = \ang{315}\),
which is the average projected axis of the knot outflow,
and in the sense that would tend to reduce the difference between the two sides of the outflow.
The proper motion measurements are repeated under this worst-case scenario,
yielding \(t_{\text{kin}}(\AxP{E}) = \SI{3.7 \pm 0.5}{kyr}\) 
versus \(t_{\text{kin}}(\AxM{E}) = \SI{2.3 \pm 0.3}{kyr}\).
The difference between the timescales of the positive and negative axes is now smaller, \(\SI{1.4 \pm 0.6}{kyr}\),
but it is still significant at the \(2\sigma\) level.
We therefore conclude that the redshifted knots truly were ejected
earlier than the blueshifted knots on average,
although,
after taking into account all sources of uncertainty,
we cannot exclude some temporal overlap between individual features. 
Note that any breakdown of our auxiliary assumptions
(strictly radial flow, no acceleration or deceleration of knots)
would not change this conclusion unless it acted differentially on the two sides of the outflow.
